Unknown

### 2024-03-18 ms/ms.qmd
working on model description

We tested competing predictions through a combination of model selection and parameter estimation from the posterior of selected models. We started with a base model that included fixed effects of light intensity and light treatment on \aax, a random effect of accession on \aax, and a linear regression of PAR on accession-level \aax. We next compared the fit of the base model to a more complex with an interaction between light intensity and light treatment using LOOIC with the \textit{R} package **loo** version `r loo_version` [@vehtari_practical_2017]. These comparisons allowed us to test the main predictions of each hypothesis and for a reinforcing interactions between assimilatory and plastic hypotheses (tab:predictions). However, these models cannot test predictions when there is an interaction with the constitutive hypothesis, because this hypothesis posits accession-levels variation in responses to light intensity and/or light treatment. Therefore, we tested for significant variation among accessions in light intensity and light treatment by comparing LOOIC values of models with and without random interactions between these factors and accession.

>>>>

We tested competing predictions through a combination of model selection and parameter estimation from the posterior of selected models. We started with a base model that includes fixed effects of light intensity and light treatment on \aax, a random effect of accession on \aax, and a linear regression of PAR on accession-level \aax. We next compared the fit of the base model to a more complex with an interaction between light intensity and light treatment using LOOIC with the \textit{R} package **loo** version `r loo_version` [@vehtari_practical_2017]. These comparisons allowed us to test the main predictions of each hypothesis and for a reinforcing interactions between assimilatory and plastic hypotheses (tab:predictions). However, these models cannot test predictions when there is an interaction with the constitutive hypothesis, because this hypothesis posits accession-levels variation in responses to light intensity and/or light treatment. Therefore, we tested for significant variation among accessions in light intensity and light treatment by comparing LOOIC values of models with and without random interactions between these factors and accession.

| Hypothesis   | Prediction | Model |
|--------------|------------|------------------|
| Assimilatory |  | base model |
| Plastic      |  | base model |
| Constitutive |  | base model |
| Assimilatory * Plastic |  | + intensity $\times$ treatment |
| Assimilatory * Constitutive |  | + accession $\times$ intensity (random) |
| Plastic * Constitutive |  | + accession $\times$ treatment (random) |
| Assimilatory * Plastic * Constitutive |  | + accession $\times$ intensity $\times$ treatment (random) |
